---
title: "Tests_and_Comparisons"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Tests_and_Comparisons}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(EGeis625)
```

To compare our function to the base r linear regression function, first we will make a model using the lin_reg() function in the EGeis625 package:
```{r}
package_model <- lin_reg(mpg~disp + cyl + hp + drat + wt, mtcars)
```

Then, we will run an identical model using the base r ls() function:
```{r}
base_r_model <- lm(mpg~disp + cyl + hp + drat + wt, data = mtcars)
summary(base_r_model)
```

Comparing the values of the lin_reg() output with the values of the lm() output:
```{r}
#Test if all of the coefficients are the same (or very similar)
all.equal(as.numeric(package_model$Coefficient), as.numeric(base_r_model$coefficients))

#Test if  all of the standard error values are the same (or very similar)
all.equal(as.numeric(package_model$StandardError), as.numeric(coef(summary(base_r_model))[, "Std. Error"]))

#Test if all of the test statistics are the same (or very similar)
all.equal(as.numeric(package_model$TStatistic), as.numeric(coef(summary(base_r_model))[, "t value"]))

#Test if all of the p-values are the same (or very similar)
all.equal(as.numeric(package_model$PValue), as.numeric(coef(summary(base_r_model))[, "Pr(>|t|)"]))
```

Comparing the amount of time it takes to run lin_reg() with the amount of time it takes to run lm():
```{r}
bench::system_time(lin_reg(mpg~disp + cyl + hp + drat + wt, mtcars))
bench::system_time(summary(lm(mpg~disp + cyl + hp + drat + wt, data = mtcars)))
```
